Fast and optimal centroiding of faint stars

### 2015-03-22 ms/figure.tex
Update figure.tex

In order to test the accuracy of various centroiding methods, we need to to compare their 
performances against each other at saturating the Cramer-Rao lower bound. The closer an estimator is to saturating 
the CRLB, the more information about the quantity that we 
need to estimate is preserved. A measure for closeness of an estimator to 
saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
with the CRLB.

@@

Given the PSF model that we have adopted for our simulations, we can derive
 an expression for the CRLB as a function of the size, and SNR of stars.
 We know that the CRLB is given by the inverse of 
the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
 it is sufficient to compute the Fisher matrix.
Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
of the Fisher matrix $\mathcal{F}_{ij}$ are given by
\beq
\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
\label{fisher}
\eeq

>>>>

In order to test the accuracy of various centroiding methods, we need to to compare their 
performances against each other at saturating the Cramer-Rao lower bound on centroiding error. 
The closer an estimator is to saturating 
the CRLB, the more information about the quantity that we 
need to estimate is preserved. A measure for closeness of an estimator to 
saturating the CRLB is comparison of the root-mean-squared-error of that estimator 
with the CRLB.

The CRLB is given by the inverse of 
the Fisher information matrix $\mathcal{F}$. Thus, in order to find the CRLB,
 it is sufficient to compute the Fisher matrix.
Let us assume that we have $M$ observables $\{f_{1}, ... , f_{M}\}$, each
related to $B$ model parameters $\{\theta_{1} , ... , \theta_{B}\}$. Assuming
uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
of the Fisher matrix $\mathcal{F}_{ij}$ are given by
\beq
\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
\label{fisher}
\eeq

@@

Given the PSF model that we have adopted for our simulations, we can derive
 an expression for the CRLB as a function of the size, and SNR of stars.
